% LaTeX resume using res.cls
\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textwidth}{5.1in} % set width of text portion

\usepackage{hyperref}
\begin{document}
% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Lucas J. Sterzinger}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{Address and Phone Censored for GitHub}


\begin{resume}
 
% \section{OBJECTIVE}  A position in the field of computers with special 
%                 interests in business applications programming, 
%                 information processing, and management systems. 
 

\section{EDUCATION} 

                {\sl \textbf{PhD},} Atmospheric Science \hfill 2017 - Present \\ 
                University of California, Davis, Davis, CA \\ 
                Anticipated: Spring 2022

                {\sl \textbf{Bachelor of Science},} Atmospheric Sciences \\
                      % \sl will be bold italic in New Century Schoolbook (or
	              % any postscript font) and just slanted in
		      %	Computer Modern (default) font
                2012 - 2017\\
                University of North Dakota, Grand Forks, ND \\
                Minor: Mathematics 
 
                {\sl \textbf{Bachelor of Science},} Aeronautics \\
                2012 - 2017 \\
                University of North Dakota, Grand Forks, ND

 
\section{COMPUTER \\ SKILLS} 
                {\sl Languages \& Software:} Python, MATLAB, Fortran, C \\
                {\sl Operating Systems:} Unix/Linux, MacOS, Windows
 
\section{WORK EXPERIENCE} 
                {\sl \textbf{Graduate Student Researcher}} \hfill 2017 - Present \\
                Atmospheric Science Graduate Group, UC Davis \\
                Dr. Adele Igel, Faculty Advisor \\
                \begin{itemize}
                    \item Works on various research related to cloud and precipitation physics. Projects include:
                    \begin{itemize} \itemsep -2pt
                        \item Effect of ice crystal habit (shape) on orographic snowfall in the Sierra Nevada Mountains (Internal Funding)
                        \item Examining the relationship between mixed-phase Arctic cloud dissipation and aerosol properties (Department of Energy Funding)
                    \end{itemize}
                \end{itemize}

                {\sl \textbf{Undergraduate Research Assistant}} \hfill 2016-2017 \\
                Dept. of Atmospheric Sciences, University of N. Dakota \\
                Dr. Gretchen Mullendore, Faculty Advisor \\
                \begin{itemize}\itemsep -2pt
                    \item Worked on the “Big Weather Web” project examining potential uses for cloud infrastructure for numerical weather prediction.
                \end{itemize}

                {\sl \textbf{Undergraduate Teaching Assistant}} \hfill 2015-2017 \\
                Dept. of Atmospheric Sciences, University of N. Dakota \\
                \begin{itemize}\itemsep -2pt
                    \item Independently taught Introduction to Meteorology lab, complete with weekly lectures and laboratory experiments.
                    
                \end{itemize}

                {\sl \textbf{Technical Support Specialist}} \hfill 2012-2017 \\
                Univ. of N. Dakota School of Medicine and Health Sciences \\
                \begin{itemize} \itemsep -2pt
                    \item Responsible  for  direct  technology  support  to  faculty,  staff,  and  students.  Also  worked  on managing video conference sytems, networks, and servers.

                \end{itemize}
\section{PUBLICATIONS}
                {\sl \textbf{The Effects of Ice Habit on Orographic Snowfall}} \hfill 2020 (\textit{Anticipated}) \\
                Research Paper - In Preparation 

                {\sl \textbf{Effect of Ice Habit on Modeled \\ Predictions of Orographic Precipitation [Poster]}} \hfill Dec. 2019 \\
                American Geophysics Union Fall Meeting 2019

                {\sl \textbf{Effects of Ice Habit on Sierra Nevada Snowfall \\ and Implications for Climate Change [Poster]}} \hfill Dec. 2018 \\
                American Geophysics Union Fall Meeting 2018

                {\sl \textbf{Models in the Cloud: A Cost Exploration \\ of Cloud Computing for the Atmospheric Sciences}} \hfill Nov. 2017 \\
                News@Unidata Blog \\
                \href{https://www.unidata.ucar.edu/blogs/news/entry/models-in-the-cloud-a}{https://www.unidata.ucar.edu/blogs/news/entry/models-in-the-cloud-a}

\section{ORGS}            
                {American Meteorological Society} \\
                {American Geophysics Unions}

\section{LANGUAGES}
                English \\
                French (Bilingual Fluency) \\
                German (2 years of courses) \\
                Russian (1 semester of courses)

\section{REFERENCES} 
                Available upon request

\end{resume}
\end{document}




